---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```
# pacs

<!-- badges: start -->
<!-- badges: end -->

Because the PACS system was adopted after the surveillance had already started,
and because all the data collected prior PACS adoption have not been all entered
in the PACS system yet, the data are in several files in the `raw_data/IPL PACS`
folder of the DropBox Ecomore2 folder:

* `pre-PACS.xlsx` that contains data from aterial **\#1** to material
  **\#3718** and which is the data that were entered before adopting PACS at IPL;
* `PACS.xls` that contains data from material **\#3370** to Material **\#7463**
  and which is the data that were entered directly into PACS and retrieved from it;
* `pacs ID 7464-ID8292_2018-10-02.xlsx` weekly update.

These files will be loaded into the `prepacs` (`pre-PACS.xlsx`) and `postpacs`
(`PACS.xls` and `pacs ID 7464-ID8292_2018-10-02.xlsx`) data frames and binded
together in the `pacs` data frame. After merging with the GPS data (see
[here](https://github.com/ecomore2/gps)), the data are patched with corrections:

* `ages_2018-09-25.xlsx` that contains correction patch on ages;
* `Villages a retrouver.xlsx` that contains correction patch on villages names.

The cleaned and reshaped data are saved to the `data\pacs.csv` CSV file that can
be copy-pasted from [here]() or downloaded directly from R into a data frame:

```{r}
##
```


