---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

# PACS data

<!-- badges: start -->
<!-- badges: end -->

PACS (Pathogen Asset Control System) is the name of the data system used at
Institut Pasteur du Laos. In the context of the [Ecomore2](http://www.ecomore.org)
project, PACS is the source of epidemiological data. It basically contains one
line per sample (here, in most of cases, a sample corresponds to a case) with
age, gender, time, space, confirmation test and serotype information.

Because the PACS system was adopted after the surveillance had already started,
and because all the data collected prior PACS adoption have not been all entered
in the PACS system yet, the data are in several files in the `raw_data/IPL PACS`
folder of the DropBox Ecomore2 folder:

* `pre-PACS.xlsx` that contains data from aterial **\#1** to material
  **\#3718** and which is the data that were entered before adopting PACS at IPL;
* `PACS.xls` that contains data from material **\#3370** to Material **\#7463**
  and which is the data that were entered directly into PACS and retrieved from it;
* `pacs ID 7464-ID8292_2018-10-02.xlsx` weekly update.

In the [cleaning pipeline](https://ecomore2.github.io/pacs/make_data.html), these
files are loaded into the `prepacs` (`pre-PACS.xlsx`) and `postpacs`
(`PACS.xls` and `pacs ID 7464-ID8292_2018-10-02.xlsx`) data frames and binded
together in the `pacs` data frame. The data are patched with corrections:

* `ages_2018-09-25.xlsx` that contains correction patch on ages;
* `Villages a retrouver.xlsx` that contains correction patch on villages names;
* plus other dates, provinces and districts names that are patched directly in
the pipeline.

The cleaned and reshaped data are saved to the
[`data\pacs.csv`](https://raw.githubusercontent.com/ecomore2/pacs/master/data/pacs.csv)
CSV file that can be copied and paste to a text file on your computer or
downloaded directly from R into a data frame:

```{r}
if (! "readr" %in% rownames(installed.packages())) install.packages("readr")
pacs <- readr::read_csv("https://raw.githubusercontent.com/ecomore2/pacs/master/data/pacs.csv",
                        col_types = paste(c("icfnD", rep("c", 5), rep("D", 4), rep("f", 3)), collapse = ""))
```

The variables names are meaningful in themselves. A case will be considered as
confirmed if at least one of the `pcr` and `ns1` variables is positive.

The pipeline used to clean the data is [here](https://ecomore2.github.io/pacs/make_data.html).
A summary of the current state of the data set is 
[here](https://ecomore2.github.io/pacs/summarize_data.html).
